Star-galaxy Classification Using Convolutional Neural Networks

### 2016-05-17 paper/main.tex
put calibration curves side by side

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/clens_calibration_conv.pdf}
  \caption{
    Calibration curve for ConvNet as applied to the CFHTLenS data set.
    $p_{\rmn{gal}}$ is the fraction of objects that are galaxies.
    $p_{\rmn{conv}}$ is the probabilistic output generated by ConvNet.
    The dashed line displays the relationship
    $p_{\rmn{gal}} = p_{\rmn{conv}}$.
    The $1 \sigma$ error bars are computed following the method
    of \citet{paterno2004calculating}.
    }
  \label{fig:clens_calibration_conv}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/clens_calibration_tpc.pdf}
  \caption{Calibration curve for TPC as applied to the CFHTLenS data set.}
  \label{fig:clens_calibration_tpc}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{figures/sdss_calibration_conv.pdf}
  \caption{Calibration curve for ConvNet as applied to the SDSS data set.}
  \label{fig:sdss_calibration_conv}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{figures/sdss_calibration_tpc.pdf}
  \caption{Calibration curve for TPC as applied to the CFHTLenS data set.}
  \label{fig:sdss_calibration_tpc}
\end{figure}

>>>>

\begin{figure*}
  \centering
  \begin{minipage}[c]{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/clens_calibration_conv.pdf}
    \caption{
      Calibration curve for ConvNet as applied to the CFHTLenS data set.
      $p_{\rmn{gal}}$ is the fraction of objects that are galaxies.
      $p_{\rmn{conv}}$ is the probabilistic output generated by ConvNet.
      The dashed line displays the relationship
      $p_{\rmn{gal}} = p_{\rmn{conv}}$.
      The $1 \sigma$ error bars are computed following the method
      of \citet{paterno2004calculating}.
      }
    \label{fig:clens_calibration_conv}
  \end{minipage}
  \hfill
  \begin{minipage}[c]{0.49\textwidth}
    \includegraphics[width=\textwidth]{figures/clens_calibration_tpc.pdf}
    \caption{Calibration curve for TPC as applied to the CFHTLenS data set.}
    \label{fig:clens_calibration_tpc}
  \end{minipage}
\end{figure*}

@@

\begin{figure*}
  \centering
  \begin{minipage}[c]{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/sdss_calibration_conv.pdf}
    \caption{Calibration curve for ConvNet as applied to the SDSS data set.}
    \label{fig:sdss_calibration_conv}
  \end{minipage}
  \hfill
  \begin{minipage}[c]{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/sdss_calibration_tpc.pdf}
    \caption{Calibration curve for TPC as applied to the CFHTLenS data set.}
    \label{fig:sdss_calibration_tpc}
  \end{minipage}
\end{figure*}
